### 2017-05-01 paper/samplebody-journals.tex
added jupyter stuff:

In this instance the visualization makes it clear that reviews are more frequent in populated cities as we expect. However, it also shows visually the outliers. There are various businesses that have only a few reviews. In this context it is easier to identify outliers and also see that businesses concentrate in certain locations. Therefore we can reduce the dataset to only the cities that meet the threshold of businesses or total review counts.

>>>>

\quad In this instance the visualization makes it clear that reviews are more frequent in populated cities as we expect. However, it also shows visually the outliers. There are various businesses that have only a few reviews. In this context it is easier to identify outliers and also see that businesses concentrate in certain locations. Therefore we can reduce the dataset to only the cities that meet the threshold of businesses or total review counts.

\subsection{Business Categories}
    \quad In an effort to garner more information about user behavior, we needed to augment the initial data with that from the businesses and reviews, the latter of which serves as the link between the former two. In doing so, we attempted to profile the most frequent business reviewed by each user. The two troublesome business features were the user-defined ?tags? and ?categories?. The categories proved to be a more manageable problem as they are selected from a finite set of options. With numbers of selected categories ranging from two to twenty-eight out of over 1000 possible choices, we sought to reduce this high degree of dimensionality.
    \quad Sparse binary data of this kind quickly becomes unwieldy as traditional distance measures are highly prone to error. Such measures include K-Means, PCA analysis (for dimensionality reduction), DBSCAN, and Agglomerative Clustering. Typically, the computational cost is prohibitive (Plumpley, et. al., 2002) or the numerical values are highly unstable during computation. The goal in our application is to reduce the effective categorical space and classify the businesses into a narrower subset?on the order of ~50. Not surprisingly, this scenario is almost identical to that encountered when processing and analyzing large corpuses of text. Almost every form of textual representation falls into the ?bag-of-words? paradigm where vectors are used to represent each document, and each element corresponds to either the frequency of a given term in the dictionary (i.e. all words from all documents) or the binary existence of the word in the document. Since each document is highly unlikely to have an instance of all terms, the combination of these vectors results in a very large, very sparse matrix of n documents by p terms.
    \quad Much research has been done in recent years on Latent Semantic Analysis (or Indexing). This utilizes the fact that a given matrix?s Singular Value Decomposition provides us with a large degree of useful data concerning the nature of the matrix, namely which vectors and rows carry more weight as well as those with less impact. Furthermore, it provides a model through which new data can be projected onto the reduced subspace. The table below shows a sample of the reduced vector space and the first ten terms in each of the new topics.
